Adopting agile in the large: motivations, success factors and challenges

### 2014-05-09 journal/article.tex
Edited: Using two models side by side

In most cases a large organizational transformation proceeded gradually, and
during the process it was possible that the new agile model was used in parallel
with the old methods.

Ongoing projects were set up with previous development methods, and the agile
methods had to be arranged to fit with them [P8, P29].

Using the old and new models side by side was seen as problematic [P26], and
causing tensions on all organizational levels [P10].

As Scrum teams did not commit to fixed schedules teams working according to the
original model labeled them unreliable [P45].

The agile teams were required to comply with current procedures producing excess
documentation and stepping through approval gates [P20, P21]. The bureucracy of
the previous traditional model was still enforced, and management was not
convinced to lighten the process. In one case it was described that after
introducing the agile method teams were required to fill in templates of two
processes [P48].

Despite the agile introduction development was attempted to be managed in the
old waterfall fashion. O'Connor [P38] described management as ``focused on
meetings and big up front project plans''. In another case management was losing
confidence in agile because familiar reports on cost analysis and percentage
complete were not produced [P35].

A particular problem in sychronizing work between projects using different
models was that in Scrum the software design was fleshed out over time as
sprints progressed, but the waterfall model would require detailed design to be
locked early in the project [P29].

>>>>

% Using two models side by side

In most cases a large organizational transformation proceeded gradually, and
during the process it was possible that the new agile model was used in parallel
with the old methods. The arrangement of using the old and new models side by
side was seen as problematic [P26], and causing tensions on all organizational
levels [P10]. Ongoing projects had been set up with previous development
methods, and the agile methods had to be arranged to fit with them [P8, P29].
A particular problem in sychronizing work between projects using different
models was that in Scrum the software design was fleshed out over time as
sprints progressed, but the waterfall model would require detailed design to be
locked early in the project [P29].

Despite the agile introduction there were problems with management working
according to the old waterfall model. O'Connor [P38] described management as
``focused on meetings and big up front project plans'' despite agile being in
use. In another case management was losing confidence in agile because familiar
reports on cost analysis and percentage complete were not produced [P35]. As
Scrum teams did not commit to fixed schedules they were considered unreliable
according to the original model [P45].

There were also problems with duplicating management when two models were in
effect. For instance, agile teams were required to comply with current
procedures producing excess documentation and stepping through approval gates
[P20, P21]. The bureucracy of the previous traditional model was still enforced,
and management was not convinced to lighten the process. Another case describes
that after introducing the agile method teams were required to fill in templates
of two processes [P48].
